---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bayesROE

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

The goal of bayesROE is to provide an R package and Shiny application for easy
computation and visualization of Bayesian Regions of Evidence as described by Hoefler 
and Miller (2023). [OSF Project History](https://osf.io/jxnsv/)


## Installation

You can install the development version of bayesROE like so:

``` r
remotes::install_github(repo = "waidschrat/bayesROE", subdir = "pkg")
```

## Example

This is a basic example illustrates the Esketamine example for one non-inferiority and two superiority thresholds:

```{r example}
# library(bayesROE)
## basic example code
```


The resulting plot is shown here:

```{r pressure, echo = FALSE}
plot(rnorm(1000))
```
